Differential geometric algebra with Leibniz and Grassmann

### 2020-05-27 paper/paper.tex
fixed #51 fixed #68 fixed #69

\begin{definition}
	[Null-basis of projective split]
	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
An embedding space $\mb R^{p+1,q+1}$ carrying the action from the group $O(p+1,q+1)$ then has
$v_\infty^2 =0$, $v_\emptyset^2 =0$,
$v_\infty \cdot v_\emptyset = 1$,  and $v_{\infty\emptyset}^2 = 1$ with
Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
\begin{align*}
	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
\end{align*}
\end{definition}
\begin{definition}
	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
	\begin{align*}
		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
		\bigboxtimes_{k=1}^j \omega_k &= \sum_{\sigma\in S_P}\frac{(-1)^{\Pi(\sigma)}}{j!}\bigominus_k\omega_{\sigma(k)}
	\end{align*}
\end{definition}
These products satisfy various \verb`MultiVector` properties, including the associative and distributive laws.

>>>>

\begin{definition}
	[Null-basis of projective split]
	Let $v_\pm^2 = \pm1$ be a basis with $v_\infty = v_++v_-$ and $v_\emptyset = (v_--v_+)/2$
An embedding space $\mb R^{p+1,q+1}$ carrying the action from the group $O(p+1,q+1)$ then has
$v_\infty^2 =0$, $v_\emptyset^2 =0$,
$v_\infty \cdot v_\emptyset = -1$,  and $v_{\infty\emptyset}^2 = 1$ with
Minkowski plane $v_{\infty\emptyset}$ having the Hestenes-Dirac-Clifford product properties
\begin{align*}
	v_{\infty\emptyset}\ominus v_\infty &= -v_\infty, &  v_{\infty\emptyset}\ominus v_\emptyset &= v_\emptyset, \\
	v_\infty\ominus v_\emptyset &= -1 + v_{\infty\emptyset}, & v_\emptyset\ominus v_\infty &=  -1 - v_{\infty\emptyset}
\end{align*}
\end{definition}
\begin{definition}
	Symmetry properties of the tensor algebra can be characterized in terms of the geometric product by two averaging operations, which are the symmetrization $\odot$ and anti-symmetrization $\boxtimes$ operators:
	\begin{align*}
		\bigodot_{k=1}^j \omega_k &= \frac1{j!}\sum_{\sigma\in S_P}\bigominus_k\omega_{\sigma(k)}, &
		\bigboxtimes_{k=1}^j \omega_k &= \sum_{\sigma\in S_P}\frac{(-1)^{\Pi(\sigma)}}{j!}\bigominus_k\omega_{\sigma(k)}
	\end{align*}
\end{definition}
These products satisfy various \verb`MultiVector` properties, including the associative and distributive laws.
